### 2025-01-27 scripts/Paper-analysis.Rmd
one Rmarkdown for paper analysis

# Compare hard shell genes vs. accessory

@@

@@

@@

@@

>>>>

@@

## Compare hard shell genes vs. accessory

### Short palindromes (k=4, 6)

@@

### All RM targets (not included in main text)

@@

### Hard shell vs. accessory for within-range RM targets

@@

## Analysis of leading region

Some preliminary statistics about discarded PTUs (for main text).

```{r}
lr = read.csv('data/leading_region_081123.tsv', sep='\t')
plasmid.table = read.csv('data/plasmid_table.tsv', sep='\t')
retained.PTUs.lr = read.csv('data/leading-region-PTUs.txt', header=F)$V1
lr.identified.PTU.names = sort(unique(lr$PTU))
# Minimum sizes
sort(sapply(lr.identified.PTU.names, function(x) 
  min(plasmid.table[plasmid.table$PTU==x, "Size"])))
```

We discard those where the minimum size is <20kb: E1, E3, E9, E10, E14, E76. We check the maximum size per PTU:

```{r}
sort(sapply(paste0("PTU-E", c("1", "3", "9", "10", "14", "76")), function(x) 
  max(plasmid.table[plasmid.table$PTU==x, "Size"])))
```
